---
title: "lab 8"
author: "Renee LaManna"
date: "11/16/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(modelsummary)
library(corrplot)
library(here)
library(broom)

```


### Read in slo_homes.csv (from gauchosapce) 

```{r}
homes <- read_csv(here("data", "slo_homes.csv"))
```

### Create a subset w/ 4 cities

Task: create subset called "homes_subset" that only contains:
-SLO
-Atascadero
-Arroyo Grande
-Santa Maria-Orcutt

```{r}
homes_subset<- homes %>%
  filter(City %in% c("San Luis Obispo", "Atascadero", "Arroyo Grande", "Santa Maria-Orcutt"))
```

### A little exploration
Task: create a summary table that has the mean and standard deviation of home prices grouped by city and sale status

in {r, include = FALSE, eval = FALSE} eval means don't even run the code

```{r}
homes_subset %>%
  group_by(City, Status) %>%
  summarize(mean_price=mean(Price),
                       sd_price= sd(Price),
                       mean_sqft= mean(SqFt))

```


Task: explore the relationship between square footage and home price (from home_subsets) in a scatterplot

```{r}
ggplot(data = homes_subset, aes(x = SqFt, y = Price)) +
  geom_point() +
  geom_smooth(method = "lm")
  
```
-If you see outliers, yours first reaction shoiuld be "what might explain this"
- once u think about it determine if it is actually in the population or if it is a mistake


### Try a few linear models

Use multiple linear regression to investigate relationships between several predictor variables and home price

Create 2 different permuytations of this model:

(1) Price ~ City, Bedrooms, Bathrooms, SqFt, Status (lm1)
(2) Price ~ City, SqFt, Status (lm2)
(3) Try another one (lm3)

```{r}
lm1 <- lm(Price ~ City + Bedrooms + Bathrooms + SqFt + Status, data = homes_subset)
lm2 <-lm(Price ~ City + SqFt + Status, data = homes_subset)
lm3 <- lm(Price ~ Bedrooms + SqFt + Bathrooms, data = homes_subset)

# If I wanted San Luis Obispo to be the refernce level
# Use fct_relevel (in tidyverse pkg) to specify a new reference level
# First character u give it, will be chosen as reference level

new_homes_subset <- homes_subset %>% 
  mutate(City = fct_relevel(City, "San Luis Obispo"))

lm_slo <- lm(Price ~ City + SqFt, data = new_homes_subset)

```

How to interpret coefficient of Santa Maria-Orcutt. A home in Santa-Maria would sell for -260860.77 less than a similar home in Arorroy Grande IF everything else stays the same

Are some of the variables we included heavily correlated with eachother?
Yes, for example Square foot with bedroom or bathroom

R2:
Almost 54% of variance of home price is explained by variance in  this model. 
Will never have a actual model that explains 100% of variance
Telss us with variables that are included that 54% of the variance can be explained

### Explore correlations between quantitative variables

Task: make a subset called homes_quant (starting from homes_subset) thatonly contains the variables from Price through SqFt).

```{r}
homes_quant <- homes_subset %>% 
  select(Price:SqFt)

homes_corr <- cor(homes_quant)

corrplot(homes_corr, method = "ellipse")
```

### Compare AIC values
Lower AIC is better, indicate a better fit model

```{r}
AIC(lm1)
AIC(lm2)
```

### Use modelsummary() to return multiple model outputs

```{r}
modelsummary(list(lm1, lm2, lm3))
```

```{r}
plot(lm1)

```
Seeing outliers in Cooks data should align with ones in exploratory phase

### Use broom::augment() to return the predictions for existing observations

```{r}
home_predictions <-augment(lm1)

# Make a histogram of the resiuduals from this model (lm1)

ggplot(data = home_predictions, (aes(x = .resid))) +
  geom_histogram()
```

